\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-16 trunk/europa-basics.tex
cleaned up constraint-bsed planning section.

As the examples above show, a Planning problem (actions to achieve a
goal) may embed a Scheduling problem (what resources are necessary to
achieve stated goals) and both Planning and Scheduling may embed a
Constraint Satisfaction problem. % since temporal, resource and other
% kinds of constraints must be respected in most real life problems.
The relationships between Planning, Scheduling and Constraint
Satisfaction have been examined \cite{smith00} and have lead to use of
constraint reasoning in \eu as its innermost building block.

@@

\subsection{Constraint-Based Attribute and Interval Planning}
\label{sec:europa:cp}

The most common planning formulations use a propositional
representation, where the state of the world is represented by a set
of propositions (statements that can be true or false), and operators
change the truth values of these propositions \cite{gen87}. Although
these formulations are powerful and have allowed researchers to
develop numerous contributions in automated planning, there are many
classes of problem domains that are difficult to represent using this
formalism. In particular, it is hard to represent time, resources,
mutual exclusion and concurrency using propositions \comment{citation
  needed}. While CSP representations have traditionally had an edge in
formulating and representing planning problems, 
% It is straightforward to represent and reason about all of
% those elements using a CSP representation, as a result there has been
% some work on doing automated planning while taking advantage of CSP
% (TODO: ref). Traditionally, the entire planning problem is translated
% into a CSP and then solved using traditional CSP methods, this
leading to a formulation where action choices and relationships are
represented as variables and/or constraints, there are at least two
major drawbacks:

@@

Constraint-based Planning and specifically Constraint-Based Attribute
and Interval planning (CAIP) \cite{mus94,frank2003} is intended to
close that gap. On one hand, it takes advantage of a CSP
representation; on the other it uses attributes and intervals to
maintain an explicit representation of the elements relevant to
planning. \eu is an implementation of the CAIP framework.  This makes
it easier to write algorithms that search for an reason abut
plans. The main elements of CAIP are:

\begin{enumerate}
	\item Intervals: \comment{needs to be defined}
	\item Attributes:
	\item Domain Constraints an Configuration rules:
\end{enumerate}

\comment{Explain how planning problem instances and their solutions are represented}

>>>>

As the examples above show, a Planning problem (actions to achieve a
goal) may embed a Scheduling problem (what resources are necessary to
achieve stated goals) and both Planning and Scheduling may embed a
Constraint Satisfaction problem. 
The relationships between Planning, Scheduling and Constraint
Satisfaction have been examined \cite{smith00} and have lead to use of
constraint reasoning in \eu as its innermost building block.

@@

\subsection{Constraint-Based Planning}
\label{sec:europa:cp}

The most common planning formulations use a propositional
representation, where the state of the world is represented by a set
of propositions (statements that can be true or false), and operators
change the truth values of these propositions \cite{gen87}. Although
these formulations are powerful and have allowed researchers to
develop numerous contributions in automated planning, there are many
classes of problem domains that are difficult to represent using this
formalism. In particular, it is hard to represent time, resources,
mutual exclusion and concurrency using propositions \comment{citation
  needed}. 
Constraint Programming is a framework that lends itself very well to represent and reason about all of those elements \comment{Ixtet citation?},
consequently, there has been a good amount of work building automated planners that take advantage of CP techniques.
The most common approach in constraint-based planning has been to encode the entire planning problem as a CP problem, 
where action choices and relationships are represented as variables and/or constraints \comment {citations 158,519,539,556 from malik's book}.
The advantage of using a pure CP formulation is that standard CP solvers can be then used to solve the planning problem, however, this approach also has a couple of significant drawbacks:

@@

These drawbacks have been addressed by a small number of planning frameworks like Descartes \comment{citation 289,290 from malik's book}, IxTet \comment{citation  223 from Malik's book}, and CAIP (Constraint-Based Interval and Attribute Planning)\cite{mus94,frank2003}.
These frameworks take advantage of a CSP representation to deal with time and resources, at the same time maintaining an explicit representation of the elements relevant to planning (action choices, causal relationships, etc). This combination results in a planning approach that can deal with the type of constraints found in real-life problems, while allowing for intuitive problem descriptions and a natural way to express search algorithms and heuristics. \eu is an implementation of the CAIP framework. In CAIP, planning problems are specified in terms of:

\begin{enumerate}
	\item \textbf{Intervals}: entities that have a temporal scope (that is, a beginning and an  end in time) and a set of attributes. Intervals are used to represent actions and states in the planning domain. 
	\item \textbf{Variables and Constraints}: Variables represent Interval attributes and Constraints enable a direct representation of temporal, resource and any other the restrictions that a valid plan must comply with.
	\item \textbf{Domain Configuration Rules}: this is an explicit representation of the conceptual relationships between actions and states in the problem domain, for instance, for a Shopping Agent to be able to purchase a product, it must be at a location where the product is available.
\end{enumerate}

To generate plans, the CAIP framework uses a plan-space search approach \comment{cite malik's chapter 5}, where a partial plan is evolved until all open goals are achieved, and all inconsistencies are removed, the specific search algorithm used by \eu will be covered in detail below.
